Empowering the use of preprints in ecology and evolution: an exploration of the first 1000 *EcoEvoRxiv* preprints

### 2023-10-15 ms/ms.qmd
Updated numbers

  # Check success. Should be 1216. Yes
    dupl <- data %>%
            group_by(title) %>% 
            summarise(n = n()) %>% 
            filter(n > 1)

@@

We downloaded metadata on the `r pr` preprints currently available on *EcoEvoRxiv* (as of the `r gsub("UTC", "", dates[2])`).

>>>>

  # Check success. Should be 1216. Yes
    dupl2 <- data %>%
            group_by(title) %>% 
            summarise(n = n()) %>% 
            filter(n > 1)

@@

We downloaded metadata on the `r pr` preprints currently available on *EcoEvoRxiv* (as of the `r gsub("UTC", "", dates[2])`), after removing `r dim(dupl)[1]` duplicate titles suggesting a few authors created multiple submissons for the same preprint rather than simply updated an existing submission.
